\sout{Machine Learning for Global Conquest} \\ Multimatrices and Their Derivatives

### 2021-03-03 Math/book.tex
Havent saved in a while.

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
\DeclareMathOperator{\Tran}{Tran}
\DeclareMathOperator{\Part}{Part}
\DeclareMathOperator{\SoS}{\mathbb{S}}
\DeclareMathOperator{\Softmax}{Softmax}
\DeclareMathOperator{\Sum}{\Sigma}
\DeclareMathOperator{\remainder}{mod}
\DeclareMathOperator{\RMult}{RMult}
\DeclareMathOperator{\LMult}{LMult}
\DeclareMathOperator{\Idx}{Idx}
\DeclareMathOperator{\size}{size}
\DeclareMathOperator{\FFT}{FFT}
\DeclareMathOperator{\IFFT}{IFFT}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}
\newcommand{\dmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\,\bullet\,}$}}}
\newcommand{\mconcat}[1]{\text{\raisebox{1ex}{$\underset{#1}{\oplus}$}}}
\newcommand{\shape}[1]{\left|#1\right|}

@@

We can define the total derivative for those cases as well.

\begin{definition}[Scalar on Multimatrix Derivative]
\label{sm_derivative}
Let $f(X)$ be some function from $\mathbb{R}^{\vec{x}}$ to $\mathbb{R}$.
The complete derivative of $f$ with respect to $X$ is therefore in
$\mathbb{R}^{\vec{x}}$. That is,
\begin{align*}
f(X) &\in \mathbb{R} \\
\shape{X} &= \vec{x} \\
\shape{\frac{df}{dX}} &= \vec{x}
\end{align*}
\[
\forall \bar{x} \in \Dim(\vec{x}):
        \frac{df}{dX}[\bar{x}] =
        \frac{\partial f}{\partial X[\bar{x}]}
\]
\end{definition}

\begin{definition}[Multimatrix on Scalar Derivative]
\label{ms_derivative}
Let $F(x)$ be some function from $\mathbb{R}$ to $\mathbb{R}^{\vec{f}}$.
The complete derivative of $F$ with respect to $X$ is therefore in
$\mathbb{R}^{\vec{f}}$. That is,
\begin{align*}
\shape{F(x)} &= \vec{f} \\
x &\in \mathbb{R} \\
\shape{\frac{dF}{dx}} &= \vec{f}
\end{align*}
\[
\forall \bar{f} \in \Dim(\vec{f}):
        \frac{dF}{dx}[\bar{f}] =
        \frac{\partial F[\bar{f}]}{\partial x}
\]
\end{definition}

@@

Easily done. The hard part isn't doing the calculation. The hard part is reframing the
damn problem in your head as its geometric or `systems of equations' equivalent so that
the operation is at least somewhat intuitive.

So now consider how we would multiply two matrices $A$ and $B$ if they had more
than two dimensions. Which doesn't really leverage either of those intuitive
approaches. Let's use a concrete example to make the problems more structurally sound.

@@

\begin{definition}[Multimatrix Multiplication]
\label{mm_mult}
Let $A$ and $B$ be multimatrices such that $\shape{A} = \vec{a} \oplus \vec{c}$,
$\shape{B} = \vec{c} \oplus \vec{b}$, and $\shape{\vec{c}} = n$ with
$n \in \{0\} \cup \mathbb{N}$. We shall call $n$ the `size' or the `width'
or the `overlap' of the multiplication operation.
The shape of the result is defined, $\shape{A \mmult{n} B} = \vec{a} \oplus \vec{b}$
and the value of the result is defined,
\[
\forall \bar{a} \in \Dim(\vec{a}), \bar{b} \in \Dim(\vec{b}):
(A \mmult{n}  B)[\bar{a} \oplus \bar{b}] =
\sum_{\forall \bar{c} \in \Dim(\vec{c})}
  A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}]
\]
\end{definition}

@@

Given $\shape{A}$ and $\shape{B}$, and by our definition of multimatrix multiplication,
you can see that $\shape{A \mmult{2} B} = \left<2, 2\right>$. And the values of the
resulting multimatrix are defined:

@@

It's important to notice that this operation is identical to standard
matrix multiplication for two dimensional multimatrices. For instance,
if $A$ and $B$ are two dimensional multimatrices with shapes
$\shape{A} = \left<l_a, r_a\right>$ and $\shape{B} = \left<l_b, r_b\right>$
their product $A \mmult{1} B$ is valid if and only if $r_a = l_b$ and
the result is of shape $\shape{A \mmult{1} B} = \left<l_a, r_b\right>$.
And of course, the value at each index
$\left<l_c, r_c\right> \in \Dim(\shape{A \mmult{1} B})$ is,
\[
  (A \mmult{1} B)[l_c, r_c]
  =
  \sum_{\forall 1 \le x \le r_a} 
  A[l_c, x] B[x, r_c]
\]
All of which would be the same if this was regular matrix multiplication.

@@

Note that those inverses are defined as sets of operations, not individual operations. 
You'll see why in a bit but to clear up any early confusion you should note that multimatrix
multiplicative inverses aren't unique. For example, $\RMult[2,\Ident^2(\left<2,2\right>)]$ has
two multiplicative inverse I can think of off the top of my head;
$\RMult[2,\Ident^2(\left<2,2\right)]$ or
$\RMult[1,\Ident^2(\left<2\right>)]$.

@@

@@

\begin{theorem}[Hadamard Product Associativity]
Let $A$, $B$, and $C$ be multimatrices such that $\shape{A} = \vec{a} \oplus \vec{m}$,
$\shape{B} = \vec{m} \oplus \vec{b} \oplus \vec{n}$ and $\shape{C} = \vec{n} \oplus \vec{c}$,
where $\shape{\vec{m}} = m$ and $\shape{\vec{n}} = n$.
Then $(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
\end{theorem}
\begin{proof}
For all $\bar{a} \in \Dim(\vec{a})$, etc,
\begin{align*}
((A \dmult{m} B) \dmult{n} C)[\bar{a} \oplus \bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}]
  &= (A \dmult{m} B)[\bar{a} \oplus \bar{m} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
  &= (A[\bar{a} \oplus \bar{m}] B[\bar{m} \oplus \bar{b} \oplus \bar{n}]) C[\bar{n} \oplus \bar{c}] \\
  &= A[\bar{a} \oplus \bar{m}] (B[\bar{m} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}]) \\
  &= A[\bar{a} \oplus \bar{m}] (B \dmult{n} C)[\bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}] \\
  &= (A \dmult{m} (B \dmult{n} C))[\bar{a} \oplus \bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}]
\end{align*}
\end{proof}

\begin{theorem}[Equivalent Hadamard Product and Multiplication Chains]
When $X_1 \ldots X_{m-1}$ are all in $\mathbb{R}^{\vec{x}}$ and
$\shape{X_m} = \vec{x} \oplus \vec{r}$ for any $\vec{r}$,
\[
  (((\Ident^n(\vec{x})
  \mmult{\shape{\vec{x}}} X_1) \mmult{\shape{\vec{x}}} X_2) \mmult{\shape{\vec{x}}} X_3)
  \ldots X_m
  =
  \Ident^{n-m}(\vec{x})
  \dmult{\shape{\vec{x}}} X_1 \dmult{\shape{\vec{x}}} X_2 \dmult{\shape{\vec{x}}} X_3
  \ldots X_m
\]
And when $X_2 \ldots X_m$ are all in $\mathbb{R}^{\vec{x}}$ and
$\shape{X_1} = \vec{l} \oplus \vec{x}$ for any $\vec{l}$,
\[
  X_1 \mmult{\shape{\vec{x}}} (X_2 \mmult{\shape{\vec{x}}} (X_3
  \ldots (X_m \mmult{\shape{\vec{x}}} 
  \Ident^n(\vec{x}))))
  =
  X_1 \dmult{\shape{\vec{x}}} X_2 \dmult{\shape{\vec{x}}} X_3
  \ldots X_m \dmult{\shape{\vec{x}}} 
  \Ident^{n-m}(\vec{x})
\]
\end{theorem}
\begin{proof}
TODO 
\end{proof}

>>>>

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
\DeclareMathOperator{\Tran}{Tran}
\DeclareMathOperator{\Part}{Part}
\DeclareMathOperator{\SoS}{\mathbb{S}}
\DeclareMathOperator{\Softmax}{Softmax}
\DeclareMathOperator{\Sum}{\Sigma}
\DeclareMathOperator{\remainder}{mod}
\DeclareMathOperator{\RMult}{RMult}
\DeclareMathOperator{\LMult}{LMult}
\DeclareMathOperator{\Idx}{Idx}
\DeclareMathOperator{\size}{size}
\DeclareMathOperator{\FFT}{FFT}
\DeclareMathOperator{\IFFT}{IFFT}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}
\newcommand{\dmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\,\bullet\,}$}}}
\newcommand{\mconcat}[1]{\text{\raisebox{1ex}{$\underset{#1}{\oplus}$}}}
\newcommand{\shape}[1]{\left|#1\right|}
\newcommand{\transpose}[2]{{#1}^{\{#2\}}}

\let\oldemptyset\emptyset
\let\emptyset\varnothing

@@

We can define the total derivative for those cases as well if we model scalar
values as multimatrices of empty shapes. That leads to the following definitions,

\begin{definition}[Scalar on Multimatrix Derivative]
\label{sm_derivative}
Let $f(X)$ be some function from $\mathbb{R}^{\vec{x}}$ to $\mathbb{R}$.
As we can model $f$ as a multimatrix of shape $\left<\right>$,
the complete derivative of $f$ with respect to $X$ is therefore in
$\mathbb{R}^{\vec{x}}$. That is,
\begin{align*}
\shape{f(X)} &= \left<\right> \\
\shape{X} &= \vec{x} \\
\shape{\frac{df}{dX}} &= \vec{x} \oplus \left<\right> = \vec{x}
\end{align*}
\[
\forall \bar{x} \in \Dim(\vec{x}):
        \frac{df}{dX}[\bar{x}] =
        \frac{\partial f}{\partial X[\bar{x}]}
\]
\end{definition}

\begin{definition}[Multimatrix on Scalar Derivative]
\label{ms_derivative}
Let $F(x)$ be some function from $\mathbb{R}$ to $\mathbb{R}^{\vec{f}}$.
As we can model $x$ as a multimatrix of shape $\left<\right>$,
the complete derivative of $F$ with respect to $x$ is therefore in
$\mathbb{R}^{\vec{f}}$. That is,
\begin{align*}
\shape{F(x)} &= \vec{f} \\
\shape{x} &= \left<\right> \\
\shape{\frac{dF}{dx}} &= \left<\right> \oplus \vec{f} = \vec{f}
\end{align*}
\[
\forall \bar{f} \in \Dim(\vec{f}):
        \frac{dF}{dx}[\bar{f}] =
        \frac{\partial F[\bar{f}]}{\partial x}
\]
\end{definition}

@@

Easily done. The hard part isn't doing the calculation. The hard part is reframing the
damn thing in your head as a geometric transformation or as part of some
systems of equations to make the operation more intuitive.

So now consider how we would multiply two matrices $A$ and $B$ if they had more
than two dimensions. Which doesn't really seem to leverage either of those intuitive
approaches. Let's use a concrete example to make the problems more structurally sound.

@@

\begin{definition}[Multimatrix Multiplication]
\label{mm_mult}
Let $A$ and $B$ be multimatrices such that $\shape{A} = \vec{a} \oplus \vec{c}$,
$\shape{B} = \vec{c} \oplus \vec{b}$, and $\shape{\vec{c}} = n$ with
$n \in \{0\} \cup \mathbb{N}$. We shall call $n$ the `size' or the `width'
or the `overlap' of the multiplication operation.
The shape of the result is defined, $\shape{A \mmult{n} B} = \vec{a} \oplus \vec{b}$
and the value of the result is defined,
\[
\forall \bar{a} \in \Dim(\vec{a}), \bar{b} \in \Dim(\vec{b}):
(A \mmult{n}  B)[\bar{a} \oplus \bar{b}] =
\sum_{\forall \bar{c} \in \Dim(\vec{c})}
  A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}]
\]

The operator $\mmult{n}$ will also be used directly on shape vectors to denote
what would happen to those shape vectors under the multimatrix multiplication operation.
Thus, for any vectors $\vec{a}$, $\vec{b}$, and $\vec{c}$,
\[ (\vec{a} \oplus \vec{c}) \mmult{\shape{\vec{c}}} (\vec{c} \oplus \vec{b}) = \vec{a} \oplus \vec{b} \]
\end{definition}

@@

Given $\shape{A}$ and $\shape{B}$, and by our definition of multimatrix multiplication,
you can see that $\shape{A \mmult{2} B} = \left<2,3,2\right> \mmult{2} \left<3,2,2\right> = \left<2, 2\right>$. And the values of the
resulting multimatrix are defined:

@@

It's important to notice that this operation is identical to standard
matrix multiplication for two dimensional multimatrices. For instance,
if $A$ and $B$ are two dimensional multimatrices with shapes
$\shape{A} = \left<l_a, r_a\right>$ and $\shape{B} = \left<l_b, r_b\right>$
their product $A \mmult{1} B$ is valid if and only if $r_a = l_b$ and
the result is of shape,
\[ \shape{A \mmult{1} B} = \left<l_a, r_a\right> \mmult{1} \left<l_b, r_b\right> = \left<l_a, r_b\right> \]
And of course, the value at each index
$\left<l_c, r_c\right> \in \Dim(\shape{A \mmult{1} B})$ is,
\[
  (A \mmult{1} B)[l_c, r_c]
  =
  \sum_{\forall 1 \le x \le r_a} 
  A[l_c, x] B[x, r_c]
\]
All of which would be the same if this was regular matrix multiplication.

TODO: explain how this type of multiplication works as a system of equations

TODO: explain how this type of multiplication works geometrically

@@

Note that those inverses are defined as sets of operations, not individual operations. 
You'll see why in a bit but to clear up any early confusion you should note that multimatrix
multiplicative inverses aren't unique. For example, $\RMult[2,\Ident^2(\left<2,2\right>)]$ has
two multiplicative inverse I can think of off the top of my head;
$\RMult[2,\Ident^2(\left<2,2\right>)]$ or
$\RMult[1,\Ident^2(\left<2\right>)]$.

@@

The Hadamard product, like the regular product, is only sometimes associative. Consider, for example,
the case where $\shape{A} = \left< 3, 2 \right>$, $\shape{B} = \left< 2 \right>$, and $\shape{C} = \left<2, 3\right>$.
Then $(A \dmult{1} B) \dmult{2} C$ is valid but $A \dmult{1} (B \dmult{2} C)$ is not because
$B \dmult{2} C$ doesn't work.

\begin{theorem}[Hadamard Product Associativity]
Let $A$, $B$, and $C$ be multimatrices and $m$ and $n$ integers such that
$m \le \shape{\shape{B}}$ and $n \le \shape{\shape{B}}$.
Then if either $(A \dmult{m} B) \dmult{n} C$ or $A \dmult{m} (B \dmult{n} C)$ is valid,
the other is also valid and
\[ (A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C) \]
\end{theorem}
\begin{proof}
\begin{ppart}
Let $A$, $B$, and $C$ be multimatrices and $m$ and $n$ integers
$m \le \shape{\shape{B}}$ and $n \le \shape{\shape{B}}$ such that
$(A \dmult{m} B) \dmult{n} C$ is valid.
We can therefore construct the following shape vectors from the definition of the Hadamard product.
\[ \shape{A \dmult{m} B} = \vec{a} \oplus \vec{m} \oplus \vec{b} \]
\[ \shape{A} = \vec{a} \oplus \vec{m} \]
\[ \shape{B} = \vec{m} \oplus \vec{b} \]
\[ \shape{(A \dmult{m} B) \dmult{n} C} = \vec{l} \oplus \vec{n} \oplus \vec{c} \]
\[ \shape{A \dmult{m} B} = \vec{l} \oplus \vec{n} \]
\[ \shape{C} = \vec{n} \oplus \vec{c} \]
Where $\shape{\vec{m}} = m$ and $\shape{\vec{n}} = n$. 
Then since $\vec{a} \oplus \vec{m} \oplus \vec{b} = \vec{l} \oplus \vec{n}$ we can divide this further into two
separate cases.
\begin{case} $\shape{\vec{b}} \ge \shape{\vec{n}}$

Then we can divide $\vec{b}$ into $\vec{b} = \vec{b}_c \oplus \vec{n}$
Therefore,
\[ \shape{B} = \vec{m} \oplus \vec{b}_c \oplus \vec{n} \]
\[ \shape{A \dmult{m} B} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} = \vec{l} \oplus \vec{n} \]
\[ \vec{l} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \]
\[ \shape{(A \dmult{m} B) \dmult{n} C} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]
So, $B \dmult{n} C$ is valid and,
\[ \shape{B \dmult{n} C} = \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]
Which means that $A \dmult{m} (B \dmult{n} C)$ is also valid and,
\[ \shape{A \dmult{m} (B \dmult{n} C)} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]

Now consider that for all $\bar{a}$, $\bar{m}$, $\bar{b}_c$, $\bar{n}$, and $\bar{c}$ in
$\Dim(\vec{a})$, $\Dim(\vec{m})$, $\Dim(\vec{b}_c)$, $\Dim(\vec{n})$ and $\Dim(\vec{c})$ respectively,
\begin{align*}
  ((A \dmult{m} B) \dmult{n} C)[\bar{a} \oplus \bar{m} \oplus \bar{b}_c \oplus \bar{n} \oplus \bar{c}]
  &=
  (A \dmult{m} B)[\bar{a} \oplus \bar{m} \oplus \bar{b}_c \oplus \bar{n}]C[\bar{n} \oplus \bar{c}] \\
  &=
  A[\bar{a} \oplus \bar{m}]B[\bar{m} \oplus \bar{b}_c \oplus \bar{n}]C[\bar{n} \oplus \bar{c}] \\
  &=
  A[\bar{a} \oplus \bar{m}](B \dmult{n} C)[\bar{m} \oplus \bar{b}_c \oplus \bar{n} \oplus \bar{c}] \\
  &=
  (A \dmult{m} (B \dmult{n} C))[\bar{a} \oplus \bar{m} \oplus \bar{b}_c \oplus \bar{n} \oplus \bar{c}]
\end{align*}

So in this case, $(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
\end{case}
\begin{case} $\shape{\vec{b}} < \shape{\vec{n}}$

Then we can divide $\vec{n}$ into $\vec{n} = \vec{n}_l \oplus \vec{b}$.
So,
\begin{align*}
  \vec{a} \oplus \vec{m} \oplus \vec{b} &= \vec{l} \oplus \vec{n}_l \oplus \vec{b} \\
  \vec{a} \oplus \vec{m} &= \vec{l} \oplus \vec{n}_l
\end{align*}

Then because we have the constraint that $n \le \shape{\shape{B}}$
\begin{align*}
  n &\le \shape{\shape{B}} \\
  \shape{\vec{n}} &\le \shape{\vec{m} \oplus \vec{b}} \\
  \shape{\vec{n}_l \oplus \vec{b}} &\le \shape{\vec{m} \oplus \vec{b}} \\
  \shape{\vec{n}_l} &\le \shape{\vec{m}}
\end{align*}

And so $\vec{m}$ can be divided into $\vec{m} = \vec{m}_l \oplus \vec{n}_l$,
resulting in,
\[ \shape{B} = \vec{m}_l \oplus \vec{n}_l \oplus \vec{b} = \vec{m}_l \oplus \vec{n} \]
So $B \dmult{n} C$ is a valid operation and,
\[ \shape{B \dmult{n} C} = \vec{m_l} \oplus \vec{n} \oplus \vec{c} = \vec{m} \oplus \vec{b} \oplus \vec{c} \]
Which further shows that $A \dmult{m} (B \dmult{n} C)$ is also a valid operation and,
\begin{align*}
  \vec{a} \oplus \vec{m} &= \vec{l} \oplus \vec{n}_l \\
  \vec{a} \oplus \vec{m}_l \oplus \vec{n}_l &= \vec{l} \oplus \vec{n}_l \\
  \vec{a} \oplus \vec{m}_l &= \vec{l}
\end{align*}
So,
\begin{align*}
  \shape{(A \dmult{m} B) \dmult{n} C}
  &= \vec{l} \oplus \vec{n} \oplus \vec{c} \\
  &= \vec{a} \oplus \vec{m}_l \oplus \vec{n}_l \oplus \vec{b} \oplus \vec{c} \\
  &= \shape{A \dmult{m} (B \dmult{n} C)}
\end{align*}

Now consider that for all $\bar{a}$, $\bar{m}_l$, $\bar{n}_l$, $\bar{b}$, and $\bar{c}$ in
$\Dim(\vec{a})$, $\Dim(\vec{m}_l)$, $\Dim(\vec{n}_l)$, $\Dim(\vec{b})$ and $\Dim(\vec{c})$ respectively,
\begin{align*}
  ((A \dmult{m} B) \dmult{n} C)[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l \oplus \bar{b} \oplus \bar{c}]
  &=
  (A \dmult{m} B)[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l \oplus \bar{b}] C[\bar{n}_l \oplus \bar{b} \oplus \bar{c}] \\
  &=
  A[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l] B[\bar{m}_l \oplus \bar{n}_l \oplus \bar{b}] C[\bar{n}_l \oplus \bar{b} \oplus \bar{c}] \\
  &=
  A[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l] (B \dmult{n} C)[\bar{m}_l \oplus \bar{n}_l \oplus \bar{b} \oplus \bar{c}] \\
  &=
  (A \dmult{m} (B \dmult{n} C))[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l \oplus \bar{b} \oplus \bar{c}]
\end{align*}
So in this case, $(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
\end{case}
\end{ppart}
\begin{ppart}
Let $A$, $B$, and $C$ be multimatrices and $m$ and $n$ integers
$m \le \shape{\shape{B}}$ and $n \le \shape{\shape{B}}$ such that
$A \dmult{m} (B \dmult{n} C)$ is valid.

We can therefore construct the following shape vectors from the definition of the Hadamard product.
\[ \shape{B \dmult{n} C} =  \vec{b} \oplus \vec{n} \oplus \vec{c} \]
\[ \shape{B} =  \vec{b} \oplus \vec{n} \]
\[ \shape{C} =  \vec{n} \oplus \vec{c} \]
\[ \shape{A \dmult{m} (B \dmult{n} C)} =  \vec{a} \oplus \vec{m} \oplus \vec{r} \]
\[ \shape{A} =  \vec{a} \oplus \vec{m} \]
\[ \shape{B \dmult{n} C} =  \vec{m} \oplus \vec{r} \]

Where $\shape{\vec{m}} = m$ and $\shape{\vec{n}} = n$. 
Then since $\vec{b} \oplus \vec{n} \oplus \vec{c} = \vec{m} \oplus \vec{r}$ we can divide this further into two
separate cases.

\setcounter{case}{0}
\begin{case} $\shape{\vec{b}} \ge \shape{\vec{m}}$

In this case we can split up $\vec{b}$ into $\vec{b} = \vec{m} \oplus \vec{b}_c$. Then,
\[ \shape{B} = \vec{m} \oplus \vec{b}_c \oplus \vec{n} \]
\[ \shape{B \dmult{n} C} = \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} = \vec{m} \oplus \vec{r} \]
\[ \vec{r} = \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]
\[ \shape{A \dmult{m} (B \dmult{n} C)} = \vec{a} \oplus \vec{m} \oplus \vec{b}_r \oplus \vec{n} \oplus \vec{c} \]

Which means that $A \dmult{m} B$ is valid and,
\[ \shape{A \dmult{m} B} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} \]
Which means that $(A \dmult{m} B) \dmult{n} C$ is also valid and,
\[ \shape{(A \dmult{m} B) \dmult{n} C} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]

Now by the same argument as part 1, case 1, it follows that $A \dmult{m} (B \dmult{n} C) = (A \dmult{m} B) \dmult{n} C$.
\end{case}
\begin{case} $\shape{\vec{b}} < \shape{\vec{m}}$

Then we can divide $\vec{m}$ into $\vec{m} = \vec{b} \oplus \vec{m}_r$.
So,
\begin{align*}
  \vec{b} \oplus \vec{n} \oplus \vec{c} &= \vec{b} \oplus \vec{m}_r \oplus \vec{r} \\
  \vec{n} \oplus \vec{c} &= \vec{m}_r \oplus \vec{r}
\end{align*}

Then because we have the constraint that $m \le \shape{\shape{B}}$
\begin{align*}
  m &\le \shape{\shape{B}} \\
  \shape{\vec{m}} &\le \shape{\vec{b} \oplus \vec{n}} \\
  \shape{\vec{b} \oplus \vec{m}_r} &\le \shape{\vec{b} \oplus \vec{n}} \\
  \shape{\vec{m}_r} &\le \shape{\vec{n}}
\end{align*}

And so $\vec{n}$ can be divided into $\vec{n} = \vec{m}_r \oplus \vec{n}_r$,
resulting in,
\[ \shape{B} = \vec{b} \oplus \vec{m}_r \oplus \vec{n}_r = \vec{m} \oplus \vec{n}_r \]
So $A \dmult{m} B$ is a valid operation and,
\[ \shape{A \dmult{m} B} = \vec{a} \oplus \vec{m} \oplus \vec{n}_r = \vec{a} \oplus \vec{b} \oplus \vec{n} \]
Which further shows that $(A \dmult{m} B) \dmult{n} C$ is also a valid operation and,
\begin{align*}
  \vec{n} \oplus \vec{c} &= \vec{m}_r \oplus \vec{r} \\
  \vec{m}_r \oplus \vec{n}_r \oplus \vec{c} &= \vec{m}_r \oplus \vec{r} \\
  \vec{n}_r \oplus \vec{c} &= \vec{r}
\end{align*}
So,
\begin{align*}
  \shape{A \dmult{m} (B \dmult{n} C)}
  &= \vec{a} \oplus \vec{m} \oplus \vec{r} \\
  &= \vec{a} \oplus \vec{b} \oplus \vec{m}_r \oplus \vec{n}_r \oplus \vec{c} \\
  &= \shape{(A \dmult{m} B) \dmult{n} C}
\end{align*}

Now consider that for all $\bar{a}$, $\bar{b}$, $\bar{m}_r$, $\bar{n}_r$, and $\bar{c}$ in
$\Dim(\vec{a})$, $\Dim(\vec{b})$, $\Dim(\vec{m}_r)$, $\Dim(\vec{n}_r)$ and $\Dim(\vec{c})$ respectively,
\begin{align*}
  (A \dmult{m} (B \dmult{n} C))[\bar{a} \oplus \bar{b} \oplus \bar{m}_r \oplus \bar{n}_r \oplus \bar{c}]
  &= A[\bar{a} \oplus \bar{b} \oplus \bar{m}_r] (B \dmult{n} C)[\bar{b} \oplus \bar{m}_r \oplus \bar{n}_r \oplus \bar{c}] \\
  &= A[\bar{a} \oplus \bar{b} \oplus \bar{m}_r] B[\bar{b} \oplus \bar{m}_r \oplus \bar{n}_r] C[\bar{m}_r \oplus \bar{n}_r \oplus \bar{c}] \\
  &= (A \dmult{m} B)[\bar{a} \oplus \bar{b} \oplus \bar{m}_r \oplus \bar{n}_r] C[\bar{m}_r \oplus \bar{n}_r \oplus \bar{c}] \\
  &= ((A \dmult{m} B) \dmult{n} C)[\bar{a} \oplus \bar{b} \oplus \bar{m}_r \oplus \bar{n}_r \oplus \bar{c}]
\end{align*}

So $A \dmult{m} (B \dmult{n} C) = (A \dmult{m} B) \dmult{n} C$.
\end{case}
\end{ppart}
Which concludes the proof, as it is now shown that in both directions when $m \le \shape{\shape{B}}$ and $n \le \shape{\shape{B}}$,
$(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
\end{proof}

@@

\begin{theorem}[Identity Multiplication and Hadamard Reductions]
Consider $\shape{X} = (k * \vec{x}) \oplus \vec{r}$ for any vectors $\vec{x}$ and $\vec{r}$
and natural number $k$. And let $n \ge k$. Then,
\[ \Ident^n(\vec{x}) \mmult{k\shape{\vec{x}}} X = \Ident^{n-k}(\vec{x}) \dmult{k\shape{\vec{x}}} X \]
